BioTime

### 2019-07-03 data-raw/biotime.Rmd
Make function for chacking names missing ID's against other providers to get synonyms that might have ids.

Do any unmatched species have matches with other providers?
```{r}
#get_match_counts(biotime_data %>% filter(is.na(id)), "sourceName")

unmatched <- biotime_data %>% filter(is.na(id)) %>% pull(sourceName) %>% unique()
providers <- c("ott", "gbif", "col", "ncbi", "wd", "iucn")

#match all the un-ID'd names to other providers, check if synonyms given by those providers match known ITIS species 
alt_names <- map_df(providers, function(name) synonyms(unmatched, name)) %>%
  drop_na(acceptedNameUsageID) %>%
  #new matches can be in either the synonym or acceptedNameUsage column, so let's combine them
  gather(type, altProviderName, synonym, acceptedNameUsage) %>%
  select(altProviderName, input) %>% 
  distinct() %>%
  drop_na(altProviderName)

#match accepted names from 
syn_res <- by_name(na.omit(unique(alt_names$altProviderName)),"itis") %>%
  drop_na(acceptedNameUsageID) %>% 
  rename(altProviderName = input) %>%
  left_join(alt_names, na_matches = "never", by = "altProviderName")

>>>>

Do any unmatched species have matches with other providers?
```{r}

#Check for potential matches from synonyms found in the other providers
syn_res <- match_providers(biotime_data, "itis")
